---
title: "Exercise_1B"
author: "Jieran Sun"
date: "10/4/2021"
output: html_document
---
\

## Exercise 1B: R Markdown Testing

\

This is the exercise for STA 1B. In this HTML document, we will configure a sample containing 100 random values from a log-normal distribution with mu=1 and sigma=0.25. This can be achieved via

```{r}
Exer1B_Sample <- rlnorm(100, meanlog=1, sdlog=0.25)
```
\

### Visualization of sample data

\
We assigned the variable as Exer1B_Sample, and now we can plot the histogram of the sample in both linear and log scale.

```{r, echo=F, fig.cap="Histogram of sample data in linear scale."}
# plot
hist(Exer1B_Sample)
```

```{r, echo=F, fig.cap="Histogram of sample data in log scale."}
# plot
hist(log(Exer1B_Sample))
```
\

### Mean and Variance Calculation

\

Let's find out the mean and the variance.

```{r}
Exer1B_Sample.mean <- mean(Exer1B_Sample) 
Exer1B_Sample.mean
```

```{r}
Exer1B_Sample.var <- var(Exer1B_Sample) 
Exer1B_Sample.var
```

And for samples in log scale, we have

```{r}
Exer1B_Sample.logmean <- mean(log(Exer1B_Sample)) 
Exer1B_Sample.logmean
```

```{r}
Exer1B_Sample.logvar <- var(log(Exer1B_Sample)) 
Exer1B_Sample.logvar
```
\

### Conclusion

\


```{r, echo=F}
print(paste0("Hence, we can draw the conclusion that the mean and variance of the sample in linear scale are ", round(Exer1B_Sample.mean, 2), " and ", round(Exer1B_Sample.var, 2), ". Similarly, in log scale, the mean and variance of the sample are estimated as ", round(Exer1B_Sample.logmean, 2), " and ", round(Exer1B_Sample.logvar, 2)))
```
